\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/triggers.tex
comment out sbo impl for now

We make use of this pattern in a willing payload such that user input can intentionally
mistrain the branch predictor by repeatedly sending valid (in-bounds) values of
\texttt{y} before sending a value that would overflow the bounds of \texttt{c}.
The speculative entry point is also chosen by the 
trigger in this scenario as \texttt{z} contains the address of the 
speculative entry point, allowing the attacker to create a ROP-style speculative 
execution path through the payload. We describe our implementation of this in
Section~\ref{tk}.

>>>>

We make use of this pattern in a willing payload such that user input can intentionally
mistrain the branch predictor by repeatedly sending valid (in-bounds) values of
\texttt{y} before sending a value that would overflow the bounds of \texttt{c}.
The speculative entry point is also chosen by the 
trigger in this scenario as \texttt{z} contains the address of the 
speculative entry point, allowing the attacker to create a ROP-style speculative 
execution path through the payload.
%We describe our implementation of this in Section~\ref{tk}.

% If it gets implemented, remove this, add that ^^^
\FigSpectreOne
We implemented an experiment to determine the number of times a branch needs to
be ``trained'' before it can be used as a speculative buffer overflow.
Figure~\ref{fig:spectre-one} shows that several hundred benign inputs are needed
to reliably be able to observe speculative buffer overflow behavior.
